Home

### 2022-03-07 analysis/index.Rmd
wflow_publish("analysis/index.Rmd")

## [Project Workflow Status](status.html) {.unnumbered}

@@

@@

Primary analysis performed by: [Jenny Sjaarda](jennysjaarda@gmail.com).

>>>>

## [Project Workflow Status](project_status.html) {.unnumbered}

@@

## [Manuscript](manuscript.html) {.unnumbered}

Document with a final summary of the analyses and tables for the manuscript.

@@

Primary analysis performed by: [Jenny Sjaarda](https://wp.unil.ch/sgg/people/jenny-sjaarda/).
